---
title: "p8105_hw5_cq2207"
author: "Carolina Q Cardoso"
date: "11/7/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(rvest)
library(ggplot2)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>%
  janitor::clean_names()

```

# Problem 1

Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement.

```{r Problem1}

#For numeric variables, you should fill in missing values with the mean of non-missing values
#For character variables, you should fill in missing values with "virginica" (Species)

fx_fill = function(x) {
  
  if (is.numeric(x))  {
    replace_na(x, mean(x, na.rm = TRUE))
  }
  
  else if (is.character(x)) {
    replace_na(x, "virginica")
  }
  
}

iris_filled = map(iris_with_missing, fx_fill) %>%
  as_tibble()


```

# Problem 2

```{r Problem2}

prob2_data =
  list.files("./datasets/", pattern = ".csv", full.names = TRUE) 

data_complete = prob2_data %>%
  map_df(read.csv) %>%
  mutate(file_name = tools::file_path_sans_ext(basename(prob2_data))) %>%
  mutate(
    subject_id = c(1:20), 
    study_arm = ifelse(subject_id == c(1:10), "control", "experimental")
  ) %>%
 select(subject_id, study_arm, file_name, everything()) %>%
 select(-file_name) %>% #used name of file to ensure observations were coded correctly as control/experimental 
pivot_longer(week_1:week_8, names_to = "week", names_prefix = "week_", values_to = "value")
 

data_complete %>%
  ggplot(aes(x = week, y = value, color = study_arm, group = subject_id)) +
  geom_point(size = 1) + geom_line() +
  geom_text(data = subset(data_complete, week == "8"), aes(label = subject_id, x = week, y = value), hjust = -.5) +
  labs(
    title = "Subject's Values by Study Arm",
    subtitle = "Weeks 1 to 8",
    x = "Time in Weeks",
    y = "Value") + 
  theme_minimal() 


```

While both the control and the experimental arms of the study varied through out the 8 weeks, the experimental arm showed a net increase in value, and finished Week 8 with higher values than the control arm and higehr values than at baseline (Week 1).


# Problem 3

1) First set the following design elements:

- Fix n=30
- Fix xi1 as draws from a standard Normal distribution
- Fix β0=2
- Fix σ2=50

2) Set β1=0. Generate 10000 datasets from the model

```{r Problem3}

set.seed(10)

sim_regression = function(beta1 = 0, beta0 = 2, n =30) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, sd = 50^(.5))
  )
  
  ls_fit = lm(y ~ x, data = sim_data) %>% broom::tidy()
  
  tibble(
    beta1_hat = ls_fit[[2,2]],
    p_value = ls_fit[[2,5]]
  )
}


sim_results = 
  rerun(10000, sim_regression(beta1=0)) %>% 
  bind_rows() 

sim_results

```

3) Repeat the above for  β1={1,2,3,4,5,6}

```{r problem3-part1}
b1_values = list( 
              "b1_1" = 1, 
              "b1_2" = 2, 
              "b1_3" = 3,
              "b1_4" = 4,
              "b1_5" = 5,
              "b1_6" = 6
              )

sim_results2 = 
  tibble(beta_1 = c(1,2,3,4,5,6)) %>% 
  mutate(
    output_lists = map(.x = b1_values, ~rerun(10000, sim_regression(beta1 = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs)
sim_results2
```

4) Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of β2 on the x axis. Describe the association between effect size and power.

```{r problem3-cont}

sim_results2 %>%
  mutate(reject = ifelse(p_value < 0.05, "yes", "no"), reject = as.factor(reject)) %>%
  group_by(beta_1, reject) %>% 
  summarize(n = n()) %>% 
  mutate(
    power = (n/sum(n))
  ) %>% 
  filter(reject == "yes") %>% 
  ggplot(aes(x = beta_1, y=power, fill = power)) + 
  geom_col() + 
  labs(
    title = "Power by Effect Size Among Rejected Null Hypothesis",
    x="Effect Size (Beta1)", 
    y="Power") + 
  theme_minimal() 
  
```

As effect size incerases, power also incerases. There is a positive relationship between the two measures.


5) 
 _a. Make a plot showing the average estimate of β̂ 1 on the y axis and the true value of β1 on the x axis_.
 
 _b. Make a second plot (or overlay on the first) the average estimate of β̂ 1 only in samples for which the null was rejected on the y axis and the true value of β1 on the x axis._


```{r - problem3-plots}

plot1 = sim_results2 %>%
  group_by(beta_1) %>%
  summarize(mean_b1 = mean(beta1_hat)) 

plot2 = sim_results2 %>%
  mutate(reject = ifelse(p_value < 0.05, "yes", "no"), reject = as.factor(reject)) %>%
  group_by(beta_1, reject) %>%
  summarize(mean_b1 = mean(beta1_hat)) %>%
  filter(reject == "yes") 

ggplot(data = plot1, aes(x = beta_1, y = mean_b1, color = "All")) +
  geom_point(size = 2) + geom_point(data = plot2, aes(x = beta_1, y = mean_b1, color = "Rejected"), size = 2) +
  scale_colour_discrete(name="Sample",
                            breaks=c("All", "Rejected"),
                            labels=c("All Beta 1", "Beta 1 Where Null is Rejected")) +
  labs(
    title = "Average Estimate of Beta 1 by True Value of Beta 1 ",
    x="True Value of Beta 1", 
    y="Average Estimate of Beta 1") + 
  theme_minimal()

```

_c. Is the sample average of β̂ 1 across tests for which the null is rejected approximately equal to the true value of β1? Why or why not?_

The graph above shows a discrepancy between the average Beta 1 estimate across tests for which the null is rejected and when the true valeu of Beta 1. When the null is rejected the average estimate of Beta 1 is higher, that is, the effect size for that subset is larger than for the full sample. The difference is greater for the smaler values of Beta 1 and decreases as Beta 1 increases, because the null is rejected more frequently at larger effect sizes.  
